{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation

### 2012-02-01 paper/paper.tex
removed citation from title
removed remark

\title{{\normalsize Seminar: Formal Specification} \\[1ex]
  Security of Multithreaded Programs by Compilation\cite{Barthe07}}
\author{Pascal Wittmann, Advisor: Artem Starostin}
\institute{TU Darmstadt}

@@

\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper \cite{Barthe07} which is as follows. First the basic
terms and definitions for multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typeable in this type system is secure.
The proof that this holds is sketched in the following section.
In the last section the (by now) abstract framework is instantiated with a
concrete example.

>>>>

\title{{\normalsize Seminar: Formal Specification} \\[1ex]
  Security of Multithreaded Programs by Compilation}
\author{Pascal Wittmann, Advisor: Artem Starostin}
\institute{TU Darmstadt}

@@

\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper \cite{Barthe07} which is as follows. First the basic
terms and definitions for multithreaded programs and the scheduler are
laid. After that the notion of security we want to achieve is presented.
Along with this a skeleton of a type system is described, which ensures
that a program typeable in this type system is secure.
The proof that this holds is sketched in the following section.
In the last section the abstract framework is instantiated with a
concrete example.
